---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# check

*{check}* is yet another package to deal with assertions. It's only a proof of
concept.

*{assertive}*, *{assertthat}*,  *{ensurer}*, *{assertr}*, *{checkmate}* ... are 
more mature packages that will do the the same job.

## Installation

``` r
remotes::install_gitub("moodyudskipper/check")
```

## How it works

```{r, include = FALSE}
library(check)

# don't namespace this one! (no `::`)
set_check_fun(
  "`{var}` must be a {type} vector of length {length}." = {
      val <- get(var, env)
      is.atomic(val) && is(val, type) && length(val) == length
  }
  # we can add more
  )
```

Your functions will look like this:

```{r, error=TRUE}
hello <- function(x) {
  check(
    "`x` must be a character vector of length 1."
    # we can add more
    )
  print(paste("hello", x))
}

hello("world")

hello(c("it's", "me"))
```

* The error messages are the code, so it's very readable.
* Assertion patterns are defined for the package and are reused in different functions, 
  so it is both enforcing consistency and leaving complete flexibility to the users.
  
To do so :

* Paste `check::setup()` in an a R file of your package. It will create local 
  copies of `check::check`, `check::check_set_fun`, and a `check_funs` environment
  
* Right below define assertions using `check_set_fun(...)`

For instance have a "check.R" file containing :

```{r, eval = FALSE}
check::setup() # unnecessary if you want to test it outside of a package

# don't namespace this one! (no `::`)
set_check_fun(
  "`{var}` must be a {type} vector of length {length}." = {
      val <- get(var, env)
      is.atomic(val) && is(val, type) && length(val) == length
  }
  # we can add more
  )
```

If you forget what patterns to use, then type `check_funs$` and auto-complete
will show you what you've defined. If you misspell a pattern, `check` will suggest
the closest fit to you.

## Caveats

* A bit more setup than packages mentioned above. We could provide a `check_funs` 
  environment with some patterns usable out of the box, for most common checks.
* Doesn't currently tell you more about the problematic arguments (e.g. failing
  example above doesn't tell you that it fails because `x` is of length 2)
